---
date: "21/01/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
```


```{r readfile, include=FALSE}

best_picture <- read_csv("table/normalized_predict_picture_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_director <- read_csv("table/normalized_predict_director_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_ada_screen <- read_csv("table/normalized_predict_ada_screen_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_ori_screen <- read_csv("table/normalized_predict_ori_screen_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_actor <- read_csv("table/normalized_predict_actor_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_actress <- read_csv("table/normalized_predict_actress_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_sup_actor <- read_csv("table/normalized_predict_supporting_actor_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

best_sup_actress <- read_csv("table/normalized_predict_supporting_actress_2019.csv", col_names = c("Movie", "Chance of Winning"), skip = 1)

results <- read.csv("table/results.csv")

results <- results %>% 
  rename(
    `Model's Prediction` = Model.s.Prediction,
    `Sarah's Prediction` = Sarah.s.Prediction,
    `Actual Winner` = Actual.Winner
  )

```

# Oscar-Machine-Learning
Machine Learning model to predict the winners of the oscars

# Articles

[Part I](https://www.linkedin.com/pulse/oscar-machine-learning-model-vs-data-scientists-girlfriend-thomas-pin/)

[Part II](https://www.linkedin.com/pulse/oscar-machine-learning-model-vs-data-scientists-girlfriend-thomas-pin-1f/?published=t&trackingId=q5s3hDx5E6yG81zwH1XdjA%3D%3D)


# Results

```{r Results}
kable(results)
```

### Best Picture 2020 Predictions

```{r Best Picture}
kable(best_picture)
```

**Selected film: Joker**


##  Best Director 2020 Predictions

```{r Best Director}
kable(best_director)
```

**Selected film: Parasite**

##  Best Adaptive Screen Play 2020 Predictions

```{r Best Best Adaptive Screen Play}
kable(best_ada_screen)
```

**Selected film: The Irishman**

##  Best Orginal Screen Play 2020 Predictions

```{r Best Orginal Screen Play}
kable(best_ori_screen)
```

**Selected film: The Irishman**

##  Best Actor 2020 Predictions

```{r Best Actor}
kable(best_actor)
```

**Selected film: Marriage Story**

##  Best Actress 2020 Predictions

```{r Best Actres}
kable(best_actress)
```

**Selected film: Little Woman**

##  Best Supporting Actor 2020 Predictions

```{r Best Supporting Actor}
kable(best_sup_actor)
```

**Selected film: Once Upon a Time… in Hollywood**

##  Best Supporting Actress 2020 Predictions

```{r Best Supporting Actress}
kable(best_sup_actress)
```

**Selected film: Marriage Story**
